### 2016-07-11 Renormalization.tex
some changes

RenConst[dZGlL1] := xZfL1[F[15], 0]
RenConst[dZGlR1] := xZfR1[F[15], 0]
RenConst[dZbarGlL1] := dZGlR1
RenConst[dZbarGlR1] := dZGlL1
RenConst[dMGl1] := MassRC[F[15]]

@@

RenConst[dZGG1] := FieldRC[V[5]]
\end{lstlisting}
The first two lines encode the field renormalization constant of up- and down-type quarks. The function \texttt{FieldRC} actually calculates two renormalization constants when the argument is a fermion field: the left- and right-handed part. But these terms are identical since electroweak interactions are not considered within the modelfile. It therefore suffices to just pick the first element of the list. This is achieved with the addendum $\texttt{[[1]]}$.\\
The next block of the code provides the renormalization constants of up- and down-type squarks, before the ensuing block deals with the gluino. Here, the predefined function \texttt{xZfL1} (\texttt{xZfR1}) is used to extract the field renormalization constant of the left- (right-) handed component of the Dirac-spinor.\\
Finally the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized. The necessity of the parameter \texttt{FiniteGs} will be explained shortly.\\
The result of these renormalization constants has been checked with the above calculated renormalization constants.

>>>>

RenConst[dZGlL1] := FieldRC[F[15]][[1]]
RenConst[dZGlR1] := FieldRC[F[15]][[2]]
RenConst[dZbarGlL1] := dZGlR1
RenConst[dZbarGlR1] := dZGlL1
RenConst[dMGl1] := MassRC[F[15]]

@@

RenConst[dZGG1] := FieldRC[V[5]]
\end{lstlisting}
The first two lines encode the field renormalization constant of up- and down-type quarks. The function \texttt{FieldRC} actually calculates two renormalization constants when the argument is a fermion field: the left- and right-handed part. But these terms are identical since electroweak interactions are not considered within the modelfile. It therefore suffices to just pick the first element of the list. This is achieved with the addendum \texttt{[[$1$]]}.\\
The next block of the code provides the renormalization constants of up- and down-type squarks, before the ensuing block deals with the gluino. Here, it is important to separate the calculation of the field renormalization constant of the left- (right-) handed component of the Dirac-spinor by adding \texttt{[[$1$]]} (\texttt{[[$2$]]}) at the end of \texttt{FieldRC[F[$15$]]} to pick the appropriate element of the list .\\
Finally the gauge coupling renormalization and the supersymmetry restoring counterterm are implemented, before the gluon field is renormalized. The necessity of the parameter \texttt{FiniteGs} will be explained shortly.\\
The result of these renormalization constants has been checked with the above calculated renormalization constants.
